---
title: "Set up OpenAir Visualization Functions"
author: "Ian Eykamp"
date: "10/11/2021"
output: html_document
editor_options: 
  markdown: 
    wrap: 72
---

Re-formats the dataframe loaded from the setupDatabase.R script for use
with the OpenAir package. <https://bookdown.org/david_carslaw/openair/>
Turns the tall and skinny dataframe into a wide dataframe with the
timestamp and device name as the identification variables and the
different measurements in separate columns. Also converts the timestamps
to datetime objects. Run the OpenAir functions at the end of the script
to create various visualizations.

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

### Install Packages and load sensorbot data

```{r packages}

# install or load required packages using pacman
if (!require("pacman")) install.packages("pacman")
pacman::p_load(pacman, openair, tidyverse, magrittr, hash)

# load the dataframe saved from the setupDatabase.R script
load("C:/dev/sensorbot/sensorbot.RData")

```

### Pivot and Rename key-value pairs

```{r rename}

df_processed <- 
  df %>%
  pivot_wider(
    names_from = key, 
    values_from = val
  ) %>%
  rename(
    date = ts, 
    pm1 = plantowerPM1concRaw, 
    pm25 = plantowerPM25concRaw, 
    pm10 = plantowerPM10concRaw, 
    humidity = humidity, 
    pressure = pressure, 
    temperature = temperature, 
    pm25_deq = pm25
  )
```

### Examples

The following are functions from the OpenAir library. Run them one at a
time to generate nice-looking visualizations.

```{r example1}

trendLevel(filter(df_processed, !is.na(pm25)), poll = "pm25")

```

```{r example2}

timeVariation(df_processed, poll = "pm25")

```

```{r example3}

myOutput <- timeVariation(df_processed, poll = "pm25")

plot(myOutput, subset = "hour")

```

```{r example4}
myOutput <- timeVariation(df_processed, poll = c("pm1", "pm25", "pm10"))

plot(myOutput, subset = "hour")

```

```{r example5}

calendarPlot(df_processed, poll = "pm25")

```
